Wikipedia Text Mining and Entropy Analysis

### 2018-12-18 wiki_entropy/wiki_clustering.Rmd
working on output of glm with factors

```{r WALS_imputation}
#taken from https://www.tutorialspoint.com/r/r_mean_median_mode.htm
getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}

## imputation based on Gelman & Hill Chapter 25
# http://www.stat.columbia.edu/~gelman/arm/missing.pdf
random.imp <- function(a) {
  missed <- is.na(a)
  num_missed <- sum(missed)
  a.obs <- a[!missed]
  imputed <- a
  imputed[missed] <- base::sample(a.obs, num_missed, replace=TRUE)
  return(imputed)
}

@@

wf.sub <- wals.feature(c("1A", "2A", "3A", "4A"))

@@

n.sims <- 10
for (s in 1:n.sims) {
  a1 <- wf.sub$`1A`
  a1[is.na(a1)] <- getmode(a1[!is.na(a1)])
  lm.1 <- glm(a1 ~ unlist(a2.imp, use.names = FALSE) + unlist(a2.imp, use.names = TRUE) + unlist(a2.imp, use.names = TRUE), family = binomial)
  pred.1 <- rnorm(n, predict(lm.1), sigma.hat(lm.1))
  a1.imp <- impute(wf.sub[c("1A")], pred.1)
}

>>>>

```{r Gelman}
## from http://www.stat.columbia.edu/~gelman/bda/regression.R

sigma.hat <- function (object){
  object.class <- class(object)[[1]]
  if (object.class=="lm"){
    sigma <- summary(object)$sigma
    return (sigma)
  }
  else if (object.class=="glm"){
    sigma <- summary(object, correlation=TRUE)$sigma
    return (sigma)
  }
  else if (object.class=="lmer"){
    object <- summary (object)
    fcoef <- .Call("mer_fixef", object, PACKAGE = "lme4")
    useScale <- object@devComp[8]
    ngrps <- lapply(object@flist, function(x) length(levels(x)))
    n.groupings <- length (ngrps)
    varc <- VarCorr (object, useScale=useScale)
    sc <- attr(varc, "sc")
    recorr <- lapply(varc, function(el) el@factors$correlation)
    reStdDev <- c(lapply(recorr, slot, "sd"), list(Residual = sc))
    sigmas <- as.list (rep (NA, n.groupings+1))
    sigmas[1] <- ifelse (useScale, sc, NA)
    cors <- as.list (rep (NA, n.groupings+1))
    names (sigmas) <- names (cors) <- c ("data", names (varc))
    for (k in 1:n.groupings){
      sigmas[[k+1]] <- reStdDev[[k]]
      cors[[k+1]] <- as.matrix (recorr[[k]])
      if (length (cors[[k+1]]) == 1) cors[[k+1]] <- NA
    }
    return (list (sigma=sigmas, cors=cors))
  }
}
```

```{r WALS_imputation_functions}
#taken from https://www.tutorialspoint.com/r/r_mean_median_mode.htm
getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}

## imputation based on Gelman & Hill Chapter 25
random.imp <- function(a) {
  missed <- is.na(a)
  num_missed <- sum(missed)
  a.obs <- a[!missed]
  imputed <- a
  imputed[missed] <- base::sample(a.obs, num_missed, replace=TRUE)
  return(imputed)
}

@@

get_factor <- function(cname) {
  a.imp <- wf.sub[c(cname)] %>%
    random.imp() %>%
    unlist(use.names = FALSE)
}
```

```{r WALS_imputation_code}
FEATURES <- c(1:144)
for (i in c(1:144)) {
  FEATURES[i] <- paste(FEATURES[i], "A", sep = "")
} #get all WALS features in correct syntax

wf <- wals.feature(FEATURES)
wf.sub <- wf[c("1A", "2A", "3A", "4A", "language")]
wf.sub <- wf.sub %>% 
  filter(language %in% LANGUAGES) %>%
  unique()

for (i in 1:4) {
  wf.sub[, i] <- factor(wf.sub[, i])
}

a1.imp <- get_factor("1A")
a2.imp <- get_factor("2A")
a3.imp <- get_factor("3A")
a4.imp <- get_factor("4A")

@@

n.sims <- 10
for (s in 1:n.sims) {
  a1 <- wf.sub$`1A`
  a1[is.na(a1)] <- getmode(a1[!is.na(a1)])
  lm.1 <- glm(a1 ~ a2.imp + a3.imp + a4.imp, family = "binomial")
  pred.1 <- rnorm(n, predict(lm.1), sigma.hat(lm.1)) ####
  a1.imp <- impute(wf.sub[c("1A")], pred.1)
}
